\thetitle

### 2013-06-18 tfpie/tfpie.tex
fix some bugs DVH found

class Leaf {
    Integer v;
    Leaf(Integer v) { this.v = v; }
    public Integer sum() { return this.v; }
}

class Node {
    Tree left; Integer v; Tree right;
    Node(Tree l, Integer v, Tree r) {
        this.left = l;
        this.v = v;
        this.right = r;
    }

@@

Finally, the Java portion of the class does not continue the use of
``World''-style interactive graphical
programming. \citet{local:java-world}.  Instead, our course focuses on
coverage of standard Java libraries, as well as introductory
algorithmic and data structure topics.  Continuing to use World-style
programming in motivating examples might be valuable for continuity
between the two halves of the course.

>>>>

class Leaf implements Tree {
    Integer v;
    Leaf(Integer v) { this.v = v; }
    public Integer sum() { return this.v; }
}

class Node implements Tree {
    Tree left; Integer v; Tree right;
    Node(Tree l, Integer v, Tree r) {
        this.left = l;
        this.v = v;
        this.right = r;
    }

@@

Finally, the Java portion of the class does not continue the use of
``World''-style interactive graphical programming, although a version
of the ``World'' library has been developed for Java
\cite{local:java-world}.  Instead, our course focuses on coverage of
standard Java libraries, as well as introductory algorithmic and data
structure topics.  Continuing to use World-style programming in
motivating examples might be valuable for continuity between the two
halves of the course.
